
visualization is an old method which has existed for thousands' years in human history.  You must have impressions of old maps appearing in many fairytale adventure stories. An early example of using visualization in scientific research is Leonhard Euler who used a simple graph to study the problem of the Königsberg bridges in 1763 \cite{biggs1986graph}. The study of this problem has been commonly recognized as the beginning of Graph Theory. Graphs are frequently used by computer scientists as abstractions when modeling an application problem. Cutting a graph into smaller pieces is one of the fundamental algorithmic operations. Current technology generates a massive amount of data (``Big Data") from business interactions and social exchanges (Facebook became the world's largest social networking site with more than 802 million active daily users on average for March 2014 \cite{bright2015too}). Graph partitioning technics play a key role in classifying and clustering such huge amount of data. High-performance algorithms of partitioning graphs for specific applications are always pursued.

Nowadays visualization has ever-expanding applications in science, education and engineering especially after the rapid growing on computer graphic technologies. However, few researches use visualizations to study algorithms. Visualizations are normally treated as representations of results (data visualization), while algorithm visualization is more commonly used as a method for educational purpose. There also appeared several general purpose visual tools which can be used for graph theory research, but they are usually limited to their own platforms or lack abilities to be implemented in an efficient way for algorithm research.
 
This dissertation applied the methodology of algorithm engineering to three graph partitioning problems across different areas including computer networks, social networks and arithmetics.  Not only visualizations indicate the performance of algorithm implementations of each work, but also help explore new algorithms to solve the problems. We term this research method as Visualized Algorithm Engineering since visualizations play a foundational role during the procedure.